ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-06-01 paper/paper.tex

\author{%
  Patrick Altmeyer\thanks{See also: https://www.paltmeyer.com/} \\
  Faculty of Electrical Engineering, Mathematics and Computer Science\\
  Delft University of Technology\\
  2628 XE Delft, The Netherlands \\
  \texttt{p.altmeyer@tudelft.nl} \\
  \And
  Mojtaba Farmanbar \\
  ING Netherlands \\
  1102 CT Amsterdam, The Netherlands \\
  \texttt{mojtaba.farmanbar@ing.com} \\
  \AND
  Arie van Deursen \\
  Delft University of Technology\\
  2628 XE Delft, The Netherlands \\
  \texttt{arie.vandeursen@tudelft.nl} \\
  \And
  Cynthia C. S. Liem \\
  Delft University of Technology\\
  2628 XE Delft, The Netherlands \\
  \texttt{c.c.s.liem@tudelft.nl} \\
}

>>>>

\author{%
  Anonymous Author\thanks{See also: } \\
  Faculty \\
  University \\
  Address \\
  \texttt{email} \\
  \And
  Anonymous Author\thanks{See also: } \\
  Faculty \\
  University \\
  Address \\
  \texttt{email} \\
}
